Poseidon Adventure

### 2020-06-12 docs/index.Rmd
add landing page to index
revisited calc_Z, decided not to change it

@@

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/atlantisom_landingpage.html" target="_blank">Draft atlantisom landing page for review, June 9, 2020</a>

@@

Further experiments with M, F, and Z across models and species confirm that mortality needs a lot more work:

<a href="https://sgaichas.github.io/poseidon-dev/TestCalcFandM.html" target="_blank">Why is mortality all over the map? June 12, 2020</a>
